### 2018-08-18 README.Rmd
fixes and pkgdown updates

> Targeted Data-Adaptive Estimation and Inference for Differential Methylation
> Analysis

@@

        @article{hejazi2018methyvim,
          doi = {},
          url = {},
          year  = {2018},
          month = {},
          publisher = {},
          volume = {},
          author = {Hejazi, Nima S and Phillips, Rachael V and Hubbard, Alan E
            and {van der Laan}, Mark J},
          title = {methyvim: Targeted and model-free differential methylation
            analysis in R},
          journal = {}
        }

>>>>

> Targeted, Robust, and Model-free Differential Methylation Analysis

@@

        @article{hejazi2018methyvim,
          doi = {},
          url = {},
          year  = {2018},
          month = {},
          publisher = {},
          volume = {},
          author = {Hejazi, Nima S and Phillips, Rachael V and Hubbard, Alan E
            and {van der Laan}, Mark J},
          title = {methyvim: Targeted, Robust, and Model-free Differential
            Methylation Analysis in {R}},
          journal = {}
        }
